EBASE manuscript

### 2022-12-19 manu-draft.qmd
finished apa cmp table

```{r, results = 'hide'}
library(knitr)
library(here)
library(flextable)

@@

The common set of metabolic parameters returned by the Odum, BASEmetab, and EBASE methods are net ecosystem metabolism, gross production, respiration, and gas exchange.  Pairwise comparisons of the daily estimates returned by each method were evaluated using simple summary statistics including Pearson correlation coefficients and linear regression fits to evaluate potential biases in each method.  For the latter analysis, differences in intercept suggested an overall bias in magnitude, whereas the slope was further tested to determine if the estimate was significantly different than one, suggesting a bias that depended on relative value of each observation (e.g., bias may differ between lower or higher values).  Comparisons were made for the whole year and by wet (June, July, August, September) or dry (all other months) season observations.  Results were also assessed separately for estimates based on the observed or detided disssolved oxygen time series.

@@

```{r}
#| tbl-cap: "Table 1: "  
# apacmptab
```

>>>>

```{r, results = 'hide'}
library(knitr)
library(here)
library(officer)
library(officedown)
library(flextable)

@@

The common set of metabolic parameters returned by the Odum, BASEmetab, and EBASE methods are net ecosystem metabolism, gross production, respiration, and gas exchange.  Pairwise comparisons of the daily estimates returned by each method were evaluated using simple summary statistics including Pearson correlation coefficients and linear regression fits to evaluate potential biases in each method.  For the latter analysis, differences in intercept estimates less than or greater than zero suggested a bias in magnitude, whereas differences in slope estimates less than or greater than one suggested a bias that depended on relative value of each observation (e.g., bias may differ between lower or higher values). Comparisons of the slope and estimates values to zero and one, respectively, were based on confidence intervals from the standard errors of each estimate. Results were assessed separately for estimates based on the observed or detided dissolved oxygen time series.

@@

`r run_reference(id = "apacmptab")`

```{r}
#| label: apacmptab
#| tbl-cap: "Summary statisics of daily metabolic estimates comparing Odum and BASEmetab to EBASE for net ecosystem metabolism (NEM), gross production (P), respiration (R), and gas exchange (D).  Separate comparisons are made for estimates based on observed and detided dissolved oxygen.  Summary statistics include Pearson correlation coefficients and intercept, slope, and residual standard deviation of a linear fit between the same metabolic estimates obtained from each method. Significance of the p-values for the intercept and slope indicates if the estimate is different from zero or one, respectively."
apacmptab
```
